Simulating High-Dimensional Multivariate Data

### 2021-02-24 index.Rmd
added DESCRIPTION file to manage dependencies
see the README for instructions on installing deps

```{r indexSetup, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide", cache=F}
library(bigsimr)
library(tidyverse)
library(knitr)
knitr::opts_chunk$set(eval = TRUE, echo = FALSE, cache = TRUE)
library(rmarkdown)
library(bookdown)
## setwd('~/article_bigsimr')
set.seed(09212020)
```

```{r copyBib, echo = FALSE, eval = FALSE, message=FALSE, warning=FALSE, results = "hide"}
system( 'cp ~/bib/bigsimr.bib ./.' )
```

@@

```{r countWords, echo = FALSE, eval = FALSE, message=FALSE, warning=FALSE, results = "hide"}
rmdFiles <- dir(pattern = 'Rmd$', ignore.case= T)
## rmdFiles <- rmdFiles[-grep('^_', rmdFiles)]
rmdFiles <- rmdFiles[-grep('references', rmdFiles)]
## rmdFiles <- rmdFiles[-grep('README', rmdFiles)]
## rmdFiles <- rmdFiles[-grep('article', rmdFiles)] ## after generating a single document
## wordcountaddin::word_count( rmdFiles[11] )
(counts <- sapply( rmdFiles, wordcountaddin::word_count, simplify = T ))
sum(counts)
```

@@

Another central issue lies in characterizing dependency between components in the high-dimensional random vector.
The choice of correlation in practice usually relates to the eventual analytic goal and distributional assumptions of the data (e.g., non-normal, discrete, infinite support, etc). 
<!-- Here we propose a scheme that ignores the analytic goal --- and, instead, aims to match the empirically-derived estimated correlation data and marginal characteristics.  -->
For normal data, the Pearson product-moment correlation describes the dependency perfectly.
As we will see, however, simulating arbitrary random vectors that match a target Pearson correlation matrix exactly is computationally intense [@Chen2001; @Xia17]. 
On the other hand, an analyst might consider use of nonparametric correlation measures to better characterize monotone, non-linear dependency, such as Spearman's $\rho$ and Kendall's $\tau$.
Throughout, we focus on matching these nonparametric dependency measures, as our aim lies in modeling non-normal data and these rank-based measures possess invariance properties favorable in our proposed methodology.

>>>>

```{r indexSetup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(eval = TRUE, 
                      echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      cache = TRUE)

library(tidyverse)
library(knitr)
library(printr)
library(rmarkdown)
library(bookdown)

set.seed(09212020)
```

```{r copyBib, include=FALSE, eval=FALSE}
system('cp ~/bib/bigsimr.bib ./.')
```

@@

```{r countWords, include=FALSE, eval=FALSE}
rmdFiles <- dir(pattern = 'Rmd$', ignore.case= T)
## rmdFiles <- rmdFiles[-grep('^_', rmdFiles)]
rmdFiles <- rmdFiles[-grep('references', rmdFiles)]
## rmdFiles <- rmdFiles[-grep('README', rmdFiles)]
## rmdFiles <- rmdFiles[-grep('article', rmdFiles)] ## after generating a single document
## wordcountaddin::word_count( rmdFiles[11] )
(counts <- sapply( rmdFiles, wordcountaddin::word_count, simplify = T ))
sum(counts)
```

@@

Another central issue lies in characterizing dependency between components in the high-dimensional random vector. The choice of correlation in practice usually relates to the eventual analytic goal and distributional assumptions of the data (e.g., non-normal, discrete, infinite support, etc).

<!-- Here we propose a scheme that ignores the analytic goal --- and, instead, aims to match the empirically-derived estimated correlation data and marginal characteristics.  -->

For normal data, the Pearson product-moment correlation describes the dependency perfectly. As we will see, however, simulating arbitrary random vectors that match a target Pearson correlation matrix exactly is computationally intense [@Chen2001; @Xia17]. On the other hand, an analyst might consider use of nonparametric correlation measures to better characterize monotone, non-linear dependency, such as Spearman's $\rho$ and Kendall's $\tau$. Throughout, we focus on matching these nonparametric dependency measures, as our aim lies in modeling non-normal data and these rank-based measures possess invariance properties favorable in our proposed methodology.
